\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2014-12-21 paper/subdocuments/results.Rnw
überarbeiten der conclusion

# Gini range
max(filter(df,kanton=="CH") %>% mutate(d_with_without=abs(G_steink-G_steink0)) %>% select(starts_with("d_")),na.rm=TRUE)
# 0.18

>>>>

# Gini range
max(filter(df,kanton=="CH") %>% mutate(d_with_without=abs(G_steink-G_steink0)) %>% select(starts_with("d_")),na.rm=TRUE)
max(filter(df,kanton=="CH") %>% mutate(d_with_without=abs(G_steink-G_steink_halb)) %>% select(starts_with("d_")),na.rm=TRUE)
# 0.18
